---
title: "P8105 Homework1"
author: "Yuzhe Hu"
date: "2023-09-23"
output: github_document
---

# Problem 1

```{r}
library("moderndive")
data("early_january_weather")
```

*   This dataset contains `r ncol(early_january_weather)` variables, which are `r names(early_january_weather)`.

*   The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

*   The mean of temperature is `r mean(early_january_weather$temp)`.

```{r, message = FALSE}
library(ggplot2)

# Draw the graph
scatter_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() + labs(x = "Time Hour", y = "Temperature (°C)", color = "Humidity (%)") + 
  theme_minimal() 
scatter_plot
ggsave("scatter plot.png", scatter_plot)
```
The raw data package recorded data from 1:00 a.m. on January 1, 2013 to 23:00 p.m. on January 15, 2013, with time intervals of one recording every one hour. There are three areas of interest in the above image: 

*   From the relationship between temperature and time, the daily temperatures fluctuated significantly and the overall temperature showed an increasing trend.
*   The relationship between humidity and time shows that the humidity was much higher from about January 12, 2013 to January 14, 2013 compared to the other dates. 
*   It is difficult to summarize the relationship between temperature and humidity based on visual observation of this graph, as it seems that the humidity was lower when the daily temperatures were higher in a single day. However, there are outliers from January 12, 2013 to January 14, 2013, which suggests that humidity may be more significantly affected by other factors.

# Problem 2
```{r, message = FALSE}
library(tidyverse)

# Create the data frame
df = data.frame(
  random_numeric = rnorm(10),  # Random sample from a standard Normal distribution
  logical_vector = rnorm(10) > 0,  # Logical vector indicating if elements are > 0
  character_vector = sample(letters, 10, replace = TRUE),  # Character vector of length 10
  factor_vector = as.factor(sample(1:3, 10, replace = TRUE))  # Factor vector with 3 levels
)

# Attempt to calculate the mean of each variable
mean(df$random_numeric)  # Works
mean(df$logical_vector)  # Works
mean(df$character_vector)  # Doesn't work
mean(df$factor_vector)  # Doesn't work
```
The calculation of mean works for numerical vectors and logical vectors, and doesn't work for character vectors and factor vectors. For the logical vector here, this logical vector consists of "TRUE" and "FALSE". R assigns "TURE" to 1 and "FALSE" to 0 by default, and uses this to calculate the mean of the logical vector.

Then load the tidyverse package and use the pull function. Apply the as.numeric function to the logical, character, and factor vectors, and calculate their mean.
```{r, message = FALSE}
# Load the tidyverse package
library(tidyverse)
# Apply as.numeric to the variables using pull
numeric_logical_vector <- df %>% pull(logical_vector) %>% as.numeric()
numeric_character_vector <- df %>% pull(character_vector) %>% as.numeric()
numeric_factor_vector <- df %>% pull(factor_vector) %>% as.numeric()
mean(numeric_logical_vector)# Works
mean(numeric_character_vector)# Doesn't work
mean(numeric_factor_vector)# Works
```
It can be seen that after applying the as.numeric function to the logical, character, and factor vectors, the calculation of mean works for logical vectors and factor vectors, but still doesn't work for character vectors.
