---
title: "P8105 Homework1"
author: "Yuzhe Hu"
date: "2023-09-23"
output: github_document
---

# Problem 1

```{r}
library("moderndive")
data("early_january_weather")
```

*   This dataset contains `r ncol(early_january_weather)` variables, which are `r names(early_january_weather)`.

*   The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

*   The mean of temperature is `r mean(early_january_weather$temp)`.

```{r, message = FALSE}
library(ggplot2)

# Draw the graph
scatter_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() + labs(x = "Time Hour", y = "Temperature (°C)", color = "Humidity (%)") + 
  theme_minimal() 
scatter_plot
ggsave("scatter plot.png", scatter_plot)
```
The raw data package recorded data from 1:00 a.m. on January 1, 2013 to 23:00 p.m. on January 15, 2013, with time intervals of one recording every one hour. There are three areas of interest in the above images: 

*   From the relationship between temperature and time, the daily temperatures fluctuated significantly and the overall temperature showed an increasing trend.
*   The relationship between humidity and time shows that the humidity was much higher from about January 12, 2013 to January 14, 2013 compared to the other dates. 
*   It is difficult to summarize the relationship between temperature and humidity based on visual observation of this graph, as it seems that the humidity was lower when the daily temperatures were higher in a single day. However, there are outliers from January 12, 2013 to January 14, 2013, which suggests that humidity may be more significantly affected by other factors.

